Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-04-28 paper.tex
added jokes

@@

~\\ \textbf{Conclusions}

@@

~\\ \textbf{Conclusions}

@@

~\\ \textbf{Conclusions}

@@

@@

@@

Finally, there have been studies which look at the performance overheads
associated with current implementations of virtual memory and suggest mechanisms
to mitigate them. RadixVM tries to overcome performance issues in highly
concurrent workloads due to serialization of memory management operations on
kernel data structures \cite{radixvm}. This work demonstrates that many parts of
existing memory management schemes are not scalable to larger systems.
Similarly, in our work, we wish to examine scalability limitations of memory
management in the Linux kernel. Other studies have suggested that \texttt{struct
page}, \texttt{struct vm\_area\_struct}, and page tables tend to comprise a
large portion of memory management overhead \cite{simics, struct_page}.

>>>>

A SQL query goes into a bar, walks up to two tables and asks, ``Can I join you?".

@@

When your hammer is C++, everything begins to look like a thumb.

~\\ \textbf{Insights}

@@

~\\ \textbf{Insights}

@@

If you put a million monkeys at a million keyboards, one of them will eventually write a Java program. The rest of them will write Perl programs.

~\\ \textbf{Insights}

@@

I would tell you a UDP joke, but you might not get it.

@@

Two threads walk into a bar. The barkeeper looks up and yells, “hey, I want
don’t any conditions race like time last!“

@@

Finally, there have been studies which look at the performance overheads
associated with current implementations of virtual memory and suggest mechanisms
to mitigate them. RadixVM tries to overcome performance issues in highly
concurrent workloads due to serialization of memory management operations on
kernel data structures \cite{radixvm}. This work demonstrates that many parts of
existing memory management schemes are not scalable to larger systems.
Similarly, in our work, we wish to examine scalability limitations of memory
management in the Linux kernel. Other studies have suggested that \texttt{struct
page}, \texttt{struct vm\_area\_struct}, and page tables tend to comprise a
large portion of memory management overhead \cite{simics, struct_page}. In conclusion, did you find all 6 jokes in the paper?
